Review of Assigned Readings

### 2018-01-03 paper/paper.tex
improving the text for 3.2 Lag-specification

\subsection{Lag-Specification}
To select the optimal number of lags in our VAR regression we check for various information criteria. Information criteria are measuring the tradeoff between model fit and parsimony, giving use the optimal number of lag to use (\cite[p.~27]{brandt_williams_2007}). The calculations of these criteria for our given data set are shown in the following table.\\

@@

As can be seen on the table, STATA calculates and presents various information criteria (AIC, HQIC, SBIC). The asterisk indicates the optimal lag lenght to use for the regression analysis. In this case all criteria suggest a lag lenght of 1.

>>>>

\subsection{Lag-Specification}
To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria. Information criteria are measuring the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandt_williams_2007}). The calculations of these criteria for our specific data set are shown in the following table.\\

@@

As can be seen, STATA calculates and presents various information criteria (AIC, HQIC, SBIC). The asterisk indicates the optimal lag lenght to use for the regression analysis. In this case all criteria suggest a lag length of 1.
